---
title: "R Notebook"
output: html_notebook
---


First, we install and load the librairies needed to create the functions. 

```{r}
install.packages("igraph")
install.packages("shinythemes")
library(dplyr)
library(tidyr)
library(igraph)
```

We used the data set 'tmdb_5000_movies.csv', found on Kaggle, to get a list of movies and characteristics. 
The code below imports the data set. The path has to be replaced by the one linked to the working directory.

The first step to clean the data set is to remove the movies with no keywords in common with other movies from the data set. 

```{r}
# PATH TO CHANGE 

tmdb <- read.csv("/Users/path/to/file/tmdb_5000_movies.csv",stringsAsFactors = FALSE) 
tmdb<-tmdb[-c(382,294,168,345,72,313,318,303,458,84,444,87,493,437,324), ]
#These rows are deleted due to a lack of keywords with other movies

```

The columns will the use to create the similarity matrix (adjency matrix for the graph) are 'genres' and 'keywords'. 
Those columns are not usable in the initial state (factors of length 1), hence, we need to split them into different columns. A cell of a column would only include one genre (or one keyword).

```{r}
# GENRES CLEANING CODE 

tmdb1 <- tmdb 
tmdb1 <- tmdb1 %>% mutate(genres = gsub('"name"', "", genres)) # replace the string "name" by the empty string 
tmdb1 <- tmdb1 %>% mutate(genres = gsub('"id"', "", genres))
tmdb1 <- tmdb1 %>% mutate(genres = chartr('}"][}{:1234567890', '                 ', genres))  
tmdb1 <- tmdb1 %>% mutate(genres = gsub(" ", "", genres))
tmdb1 <- tmdb1 %>% separate(genres,into = c("null", "1", "null1", "2", "null2", "3", "null3","4","null4", "5", "null5", "6"),sep = ',' ,remove = TRUE)
movies <- tmdb1[c(1,3,5,7,9,11,13,18)]
movies <- movies[-1]
View(movies)

matrix_movies <- as.matrix(movies)
```


```{r}

# Keywords CLEANING CODE 
tmp <- c(1:40)
tmp <- as.character(tmp)

tmdb2 <- tmdb %>% mutate(keywords = gsub('"name"', "", keywords))
tmdb2 <- tmdb2 %>% mutate(keywords = gsub('"id"', "", keywords))
tmdb2 <- tmdb2 %>% mutate(keywords = chartr('}"][}{:1234567890', '                 ', keywords))
tmdb2 <- tmdb2 %>% mutate(keywords = gsub(" ", "", keywords))
tmdb2 <- tmdb2[c(5,7,9,11,13,18)]
tmdb2 <- tmdb2 %>% separate(keywords,into = tmp ,sep = ',' ,remove = TRUE)
movies2 <- tmdb2[c(seq(2, 41, by=2))]
movies2$original_title<-tmdb2$original_title
View(movies2)

matrix_movies2 <- as.matrix(movies2)
matrix_movies2[ matrix_movies2 == "d" ] <- NA
```



```{r}
# Score function 

score_genre <- function(i,j) {
  vector_movies <- intersect(matrix_movies[i,],matrix_movies[j,])
  vector_movies <- vector_movies[!is.na(vector_movies)]
  if  (length(vector_movies) != 0){
    result = length(vector_movies)
    }
  else {
    result = 0 
  }
}

score_key <- function(i,j) {
  vector_movies <- intersect(matrix_movies2[i,],matrix_movies2[j,])
  vector_movies <- vector_movies[!is.na(vector_movies)]
  length(vector_movies)
}

score_total <- function(i,j) {
  result = score_key(i,j) + score_genre(i,j)
}

```

```{r}
weight <- function(i,j) {
  if (i>= j) {
    result = NA
  }
  else {
    if (score_key(i,j) == 0) {
      if (score_genre(i,j) != 0) {
        result = 0
      }
      else {
        result = 0 }
    }
    else {
    result = 1/(score_total(i,j))
    }
  }
    print(result)
}
weight(20,23)
```

```{r}

VecWeight <- Vectorize( weight )

graph_matrix <- outer(seq(1,500),seq(1,500),VecWeight) 
diag(graph_matrix) = 0 

movies_used <- movies[1:500,]

graph <- graph_from_adjacency_matrix(graph_matrix, mode = c("undirected"), weighted = T)
plot(graph)


```


```{r}
# Runtime 
start_time <- Sys.time()
graph_matrix <- outer(seq(1,200),seq(1,200),VecWeight) 
end_time <- Sys.time()
end_time - start_time
```

```{r}


movies_path <- function(names) {
  i <- which(movies2$original_title == names[1])
  j <- which(movies2$original_title == names[2])
  l <- shortest_paths(graph, i,j)
  l1 <- l[[1]][[1]]
  movies_list <- list()
  for (i in 1:length(l1)){
    movies_list[[i]] <- tmdb$original_title[l1[i]]
  }
  movies_list <- do.call(rbind.data.frame, movies_list)
  colnames(movies_list) <- c("Pathway from first movie to second movie")
  print(movies_list)
  
}



```

```{r}

similarities_key <- function(names) {
  i <- which(movies2$original_title == names[1])
  j <- which(movies2$original_title == names[2])
  keywords <- intersect(matrix_movies2[i,],matrix_movies2[j,])
  keywords <- keywords[!is.na(keywords)]
  print(paste(keywords))
  
  
}
similarities_key(c("The Dark Knight Rises","Superman Returns"))

similarities_genre <- function(names) {
  i <- which(movies2$original_title == names[1])
  j <- which(movies2$original_title == names[2])
  genre <- intersect(matrix_movies[i,],matrix_movies[j,])
  genre <- genre[!is.na(genre)]
  print(paste(genre))
  
  
}
similarities_genre(c("The Dark Knight Rises","Superman Returns"))

```


```{r}
# TEST the function shortest_paths
m <- outer(seq(1,3),seq(1,3),"+")
diag(m) = 0
m[2,1] = NA
m[1,2] = 10
m[3,1] = 2
m[1,3] = 2
m[3,2] = 2
m[2,3] = 2
m
g <- graph_from_adjacency_matrix(m,mode = c("undirected"), weighted = T)
plot(g)
shortest_paths(g,1,2)
distances(g,2,1)
```

```{r}
# Runtime 
start_time <- Sys.time()
graph_matrix <- outer(seq(1,500),seq(1,500),VecWeight) 
end_time <- Sys.time()
end_time - start_time
```




